\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{mathtools, amsmath}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% make easier to read for ATS systems
\input{glyphtounicode}
\pdfgentounicode=1

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------%
% Custom commands
\newcommand{\subItem}[1]{
  \item\small{ #1 \vspace{-2pt} }
}

\newcommand{\titledItem}[2]{
  \item[]{
    \textbf{#1}\small{: #2 \vspace{-2pt}}
  }
}


% General subheading
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

% Header template only for education section so GPA isn't in italics 
\newcommand{\resumeAltheading}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \small{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------%
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%
\begin{document}


%----------HEADING-----------------%
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \centerline{\textbf{{\Large Parsa Dastjerdi}}} \\
  \centerline{(U.S. Citizen)} \\
\end{tabular*}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  (281) 608-0811 & \href{https://www.linkedin.com/in/parsa-dastjerdi/}{\faLinkedin{ parsa-dastjerdi}} \\ 
  \href{mailto:parsadastjerdi@aggienetwork.com}{parsadastjerdi@aggienetwork.com} & \href{https://github.com/parsadastjerdi}{\faGithub{ parsadastjerdi}} \\
\end{tabular*}


%-----------EDUCATION-----------------%
\section{Education}
  \resumeSubHeadingListStart

  \resumeAltheading
    {Master of Science, Computer Engineering} {\textit{May 2021}}
    {Texas A\&M University; College Station, TX} {GPA: 3.40}

  \resumeAltheading
    {Bachelor of Science, Electrical Engineering} {\textit{May 2019}}
    {Texas A\&M University; College Station, TX} {GPA: 3.80}

    \textit{\small Magna Cum Laude, Dean's Honor Roll}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------%
\section{Experience} % this is getting cut off for some reason
  \resumeSubHeadingListStart

    \resumeSubheading
      {Amazon} {Seattle, WA}
      {Software Engineering Intern} {June 2020 - Aug 2020}
      \resumeItemListStart
        \subItem {Wrote API to compute relative difference between live and published plans in Planogram.}
        \subItem {Wrote Lambda to compute dispatch notes and labor estimation.}
        \subItem {Created accordion view for dispatch notes using AngularJS.}
        \resumeItemListEnd

    \resumeSubheading
      {Texas Instruments} {Dallas, TX}
      {Design Verification Intern} {May 2018 - Aug 2018}
      \resumeItemListStart
        \subItem {Built a Verilog-AMS to TDL translator in Python to remove manual overhead of functional verification of chips.}
        \subItem {Used translator to automate TDL generation for two production chips.}
        \resumeItemListEnd

\resumeSubHeadingListEnd


%--------SKILLS----------%
\section{Skills}
  \resumeSubHeadingListStart
    \titledItem{Languages}{Java, C++, Python, Ruby, Haskell, Javascript, SQL}
    \titledItem{Technologies}{AWS, Kubernetes, Docker, Android} 
    % lambda, step functions, dynamoDB
    % should i include DynamoDB?
    \titledItem{Frameworks}{Rails, React, PyTorch, Keras}
    \titledItem{Coursework}{Advanced Algorithms, Machine Learning, Probabilistic Graphical Models, Distributed Systems, Cryptography, Software Engineering}
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------------%
\section{Projects}  
  \resumeSubHeadingListStart  

    \resumeSubheading
      {Sports Analytics}{}
      {An integrated visualization tool for sports data analytics.}{}
      \resumeItemListStart
        \subItem{Developed visualizations using Chart.js to display statistical results generated from sports data.}
        \subItem{Developed GraphQL server with Spring Boot.}
        \subItem{Created distributed web scraper for soccer data using SportsMonks' soccer API.}
    \resumeItemListEnd

    \resumeSubheading
    {ZLP Scheduler}{}
    {Scheduling app built using Rails}{}
    \resumeItemListStart
      \subItem{Created full stack app to find an opening in student schedules}
      \subItem{Used Constraint Satisfaction (CSP) to determine optimal schedule} % don't think we actually used any CSP algos
    \resumeItemListEnd

    \resumeSubheading
      {Sobr}{}
      {Mobile application that prevents drunk driving by classifying intoxicated drivers through facial recognition.}{}
      \resumeItemListStart
        \subItem{Used an ensemble of CNNs to correctly classify intoxicated drivers at 90.68\% on the validation set.}
        \subItem{Placed 3rd out of 138 teams/800+ students and won ``Best Use of SmartCar API'' at TAMUHack 2019.}
    \resumeItemListEnd

    \resumeSubheading
    {Body Gesture Recognition (make detectron into this??)} {}
    {Texas A\&M University; Advisor: Dr. Anxiao Jiang} {}
    \resumeItemListStart
      \subItem{Researching methods to determine emotional state from body gestures directly from a video stream.}
      \subItem{Learning features from a 3D skeletal model generated using pose estimation techniques.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

\end{document}